\section{Abstract}
This report contains our findings on methods of finding the trap stiffness of an optical trap or optical tweezer setup and the conversion of an MATLAB data processing script to Python. 

Optical trapping is a technique in which a small particle is being held in place by a focussed laser beam, commonly used in the field of biophysics.

The trap stiffness in relation to laser output power was determined by imaging a particle in an optical trap and repeating this for multiple laser powers. The resulting image stacks were processed by an automated MATLAB script that tracks the movement of the bead. The resulting trap constants were then plotted for each laser power output setting. The predicted direct proportionality between the laser power and the trap constant could be observed. However, given the distance from the data to the best fit, the values for the slope coefficient is not of much use.

Due to the current Corona-virus outbreak we were unable to do the optical trap measurements ourselves so to make up for this we were tasked with rewriting part of a MATLAB script in Python. The bead tacking algorithm could not be finished due to complications for non-grid interpolation in Python. Th sub-pixel interpolation function and the symmetry centre finding function, were successfully transformed to python script. The presented Python file is capable of roughly following the symmetry centre of the bead in an optical trap, however with low accuracy. Therefore, an alternative Trackpy function is proposed as an alternative for the original tracking code.

Using the covariance matrix of the data, the values for the semi-major and semi-minor axis of the covariance ellipse were found for both data sets. The values match the theoretical inverse proportionality with respect to the laser power. The difference between the values for the major and minor axis compared to the MATLAB script shows the advantage of calculation of the trap constant using the covariance matrix. For this method incorporates the shape and direction of the optical trap.

\begin{comment}

\begin{table}[h!]
    \centering
    \begin{tabular}{|l|l|l|}
        \hline
        coefficient for & $a_x$ {[}$pN/(nm\cdot mW)${]} & $a_y$ {[}$pN/(nm \cdot mW)${]}\\ \hline
        dataset 1       & $1.382\cdot 10^{-6}$          & $1.280 \cdot 10^{-6}$\\ \hline
        dataset 2       & $1.478 \cdot 10^{-5}$         & $3.974 \cdot 10^{-6}$\\ \hline
    \end{tabular}
    \caption{The results of the linear fits for the trap stiffness as a function of laser output power. The shown $a$-factors satisfy the least squares fit of the function: $k_i = a_i \cdot P$ }
\end{table}

\end{comment}